---
output:
  html_document:
    self_contained: false
    lib_dir: libs
    css: styles.css
    toc: true
    df_print: paged
    number_sections: false
    theme: paper
    toc_float:
      collapsed: true
      smooth_scroll: true
    includes:
      before_body: markdown_intro.html
---


```{r echo = FALSE, results = "asis", message = FALSE, include = FALSE}

#Packages
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(sp)
library(raster)
library(lattice)
library(lme4)
library(sjPlot)
library(RColorBrewer)
library(wesanderson)
library(rasterVis)

#INITIAL DATA IMPORT + FORMATTING ----------------------------------------------------------------------------------------------

        #Approach 1
        approach1 <- read.csv('../../../Approach_1/Output/Albedo_Estimates/albedo_estimates_approach_1.csv', header = TRUE)
        approach1$Approach <- "Approach_1"

        #Approach 2
        approach2 <- read.csv('../../../Approach_2/Output/Albedo_Estimates/albedo_estimates_approach_2.csv', header = TRUE)
        approach2$Approach <- "Approach_2"
        
        #Approach 3
        approach3 <- read.csv('../../../Approach_3/Output/Albedo_Estimates/albedo_estimates_approach_3.csv', header = TRUE)
        approach3$Approach <- "Approach_3"
        
        #Approach 4
        approach4 <- read.csv('../../../Approach_4/Output/Albedo_Estimates/albedo_estimates_approach_4.csv', header = TRUE)
        approach4$Approach <- "Approach_4"
        
        #Merged (2-4)
        all <- rbind(approach2, approach3, approach4)
        all$Approach <- as.factor(all$Approach)
        
        #Simplified and merged (1-4)
        app_1_ps <- approach1[,c(1:7,9:14)]
        app_234_ps <- all[,c(1:7,9:14)]
        all_ps <- rbind(app_1_ps, app_234_ps)
        
        #CALCULATE TREATMENT DIFF (EXCL-OPEN)
        #Steps below for Approach 1 and Approaches 2-4 separately
        
                #APPROACH 1
        
                        #Initialize df
                        app_1_diff <- data.frame("Month" = integer(),
                                               "LocalityName" = character(),
                                               "Region" = character(),
                                               "Approach" = character(),
                                               "Diff" = double())
                        
                        #Get LocalityName's
                        approach1$LocalityName <- as.factor(approach1$LocalityName)
                        app_1_locs <- levels(approach1$LocalityName)
                        approach1$LocalityName <- as.character(approach1$LocalityName)
                        
                        #Construct approach1 'diff' df
                        for(k in 1:length(app_1_locs)){
                        
                                loc <- app_1_locs[k]
                                
                                #Define/reset temp df
                                tmp <- data.frame("Month" = integer(),
                                               "LocalityName" = character(),
                                               "Region" = character(),
                                               "Approach" = character(),
                                               "Diff" = double())
                                
                                        #Loop through months
                                        for(i in 1:12){
                                                
                                                #Month
                                                tmp[i, "Month"] <- i
                                                
                                                #LocalityName
                                                tmp[i, "LocalityName"] <- loc
                                                
                                                #Region 
                                                tmp[i, "Region"] <- all_ps$Region[all_ps$LocalityName == loc][1]
                                                
                                                #Approach
                                                tmp[i, "Approach"] <- "Approach_1"
                                                
                                                #Diff
                                                
                                                        #Exclosure value
                                                        excl <- all_ps$Composite_Albedo[all_ps$Month == i &
                                                                                        all_ps$LocalityName == loc &
                                                                                        all_ps$Treatment == "UB" &
                                                                                        all_ps$Approach == "Approach_1"]
                                                
                                                        #Open value
                                                        open <- all_ps$Composite_Albedo[all_ps$Month == i &
                                                                                        all_ps$LocalityName == loc &
                                                                                        all_ps$Treatment == "B" &
                                                                                        all_ps$Approach == "Approach_1"]
                                                        
                                                        #Diff
                                                        diff <- excl - open
                                                        
                                                        #Assign
                                                        tmp[i, "Diff"] <- diff
                                                        
                                        }

                                #Rbind
                                app_1_diff <- rbind(app_1_diff, tmp)
                                
                        }
        
        
                        
                #APPROACH 2-4
                        
                        #Initialize blank dataframe
                        all_diff <- data.frame("Month" = integer(),
                                               "LocalityName" = character(),
                                               "Region" = character(),
                                               "Approach" = character(),
                                               "Diff" = double())
                        
                        all_ps$LocalityName <- as.factor(all_ps$LocalityName)
                        locs <- levels(all_ps$LocalityName)
                        
                        all_ps$LocalityName <- as.character(all_ps$LocalityName)
        
                        for(k in 1:length(locs)){
                                
                                loc <- locs[k]
                                
                                #Define/reset temp df
                                tmp <- data.frame("Month" = integer(),
                                               "LocalityName" = character(),
                                               "Region" = character(),
                                               "Approach" = character(),
                                               "Diff" = double())
                                
                                #Loop through approaches
                                for(j in 2:4){
                                        
                                        app <- paste("Approach_", j, sep = "")
                                        
                                        #Loop through months
                                        for(i in 1:12){
                                                
                                                #Month
                                                tmp[i, "Month"] <- i
                                                
                                                #LocalityName
                                                tmp[i, "LocalityName"] <- loc
                                                
                                                #Region 
                                                tmp[i, "Region"] <- all_ps$Region[all_ps$LocalityName == loc][1]
                                                
                                                #Approach
                                                tmp[i, "Approach"] <- app
                                                
                                                #Diff
                                                
                                                        #Exclosure value
                                                        excl <- all_ps$Composite_Albedo[all_ps$Month == i &
                                                                                        all_ps$LocalityName == loc &
                                                                                        all_ps$Treatment == "exclosure" &
                                                                                        all_ps$Approach == app]
                                                
                                                        #Open value
                                                        open <- all_ps$Composite_Albedo[all_ps$Month == i &
                                                                                        all_ps$LocalityName == loc &
                                                                                        all_ps$Treatment == "open" &
                                                                                        all_ps$Approach == app]
                                                        
                                                        #Diff
                                                        diff <- excl - open
                                                        
                                                        #Assign
                                                        tmp[i, "Diff"] <- diff
                                        }
                                        
                                        #Rbind
                                        all_diff <- rbind(all_diff, tmp)
                                        
                                }
                                
                        }
        
        #RBIND both df's
        all_diff <- rbind(app_1_diff, all_diff)
        
        
#END INITIAL DATA IMPORT + FORMATTING ----------------------------------------------------------------------------------------------

```
                                
  

# Overview
This report compares the different approaches used to examine the effect of moose exclusion on surface albedo in Norwegian forests. In particular, it looks at the albedo estimates produced by Approaches 2-4 (since they use the same tree + climate data and are therefore directly comparable), as well as the albedo estimates produced by Approach 1 (which only uses data from Trøndelag in 2016).

***

# Albedo Estimates {.tabset}
Because Approaches 2-4 use seNorge and SustHerb data from the same years (which corresponds to the years in which LiDAR data was obtained for each site), these approaches should be directly comparable. As a reminder, Approach 1 only uses seNorge and SustHerb data from 2016, as 2016 is the only year with detailed DGL measurements (which are necessary to use SustHerb biomass models). Therefore, it isn't directly comparable with Approaches 2-4.

## Approach 1 {.tabset .tabset-fade .tabset-pills}

### Boxplot
``` {r echo = FALSE, eval= TRUE, message = FALSE}

        approach1$Month <- as.factor(approach1$Month)
        ggplot(data = approach1, aes(x = Month, y = Composite_Albedo, fill = Treatment)) +
                geom_boxplot() +
                ggtitle("Monthly albedo estimates for Trøndelag study sites in 2016 (n = 15)") +
                labs(x = "Month", y = "Albedo")
        
```

### Scatterplot
``` {r echo = FALSE, eval= TRUE, message = FALSE}

        approach1$Month <- as.numeric(approach1$Month)
        ggplot(data = approach1, aes(x = Month, y = Composite_Albedo, color = Treatment)) +
                geom_point(alpha = 0.3) +
                geom_smooth(se = F, lwd = 0.5, span = 0.3) +
                facet_grid(~ Approach) +
                ggtitle("Monthly albedo estimates for Trøndelag study sites in 2016 (n = 15)\n (by Approach)") +
                labs(x = "Month", y = "Albedo") +
                theme(
                        legend.position = "bottom"
                )
        
```



## Approaches 2-4 {.tabset .tabset-fade .tabset-pills}

### Boxplot
``` {r echo = FALSE, eval= TRUE, message = FALSE}

        all$Month <- as.factor(all$Month)
        ggplot(data = all, aes(x = Month, y = Composite_Albedo, fill = Treatment)) +
                geom_boxplot() +
                facet_grid(~ Approach) +
                ggtitle("Monthly albedo estimates for SustHerb study sites (n = 37)\n (by Approach)") +
                labs(x = "Month", y = "Albedo") +
                theme(
                        legend.position = "bottom"
                )
        
```

### Scatterplot
``` {r echo = FALSE, eval= TRUE, message = FALSE}

        all$Month <- as.numeric(all$Month)
        ggplot(data = all, aes(x = Month, y = Composite_Albedo, color = Treatment)) +
                geom_point(alpha = 0.3) +
                geom_smooth(se = F, lwd = 0.5, span = 0.3) +
                facet_grid(~ Approach) +
                ggtitle("Monthly albedo estimates for SustHerb study sites (n = 37)\n (by Approach)") +
                labs(x = "Month", y = "Albedo") +
                theme(
                        legend.position = "bottom"
                )
        
```

***

# Treatment Difference {.tabset}
By calculating the mean difference in albedo between open plots and exclosure (for each month), we might be able to compare Approach 1 with Approaches 2-4.

## Boxplot
``` {r echo = FALSE, eval= TRUE, message = FALSE}

        all_diff$Month <- as.factor(all_diff$Month)
        ggplot(data = all_diff, aes(x = Month, y = Diff, fill = Approach)) +
                geom_boxplot() +
                facet_grid(~ Approach) +
                ggtitle("Monthly difference in albedo (by approach)") +
                labs(x = "Month", y = "Albedo Difference\n(Excl. - Open)") +
                theme(
                        legend.position = "none"
                )
        
```

## Mean Difference
``` {r echo = FALSE, eval= TRUE, message = FALSE}

        #Calculate mean differences by approach
        mean_diff <- aggregate(all_diff$Diff, by = list(Approach = all_diff$Approach, Month = all_diff$Month), FUN = mean)
        colnames(mean_diff)[3] <- "Diff"

        mean_diff$Month <- as.integer(mean_diff$Month)
        ggplot(data = mean_diff, aes(x = Month, y = Diff, color = Approach)) +
                geom_point() +
                geom_line() +
                facet_grid(~ Approach) +
                ggtitle("Monthly mean difference in albedo (by approach)") +
                scale_x_continuous(limits = c(1,12), breaks = c(1,12)) +
                labs(x = "Month", y = "Mean Albedo Difference\n(Excl. - Open)") +
                theme(
                        legend.position = "none"
                )
        
```





***

#Next Steps?

#### Another Way to Compare?
Is there a better way that I can compare these approaches? I'd like to be able to directly compare Approach 1 (i.e. biomass models) with Approaches 2-4, but since these approaches use different data, I'm not sure if this is feasible.

#### Pick an Approach?
Would it be better to pick an approach for further analysis? Is there a way in which we could identify the approach that may be most accurate?


